---
title: "Homework 1"
author: "Kirill Lesnykh"
date: "January 19, 2019"
output:
  pdf_document: 
    keep_tex: yes
    latex_engine:  xelatex
header-includes:
  - \newfontfamily{\cyrillicfonttt}{Times New Roman}
  - \usepackage[utf8]{inputenc} 
  - \usepackage{fontspec}
  - \usepackage{polyglossia}
  - \setmainlanguage{russian} 
  - \setotherlanguage{english}
mainfont: Times New Roman
fontsize: 12pt
---


```{r setup, include=FALSE}
Sys.setlocale(locale = "en_RU.UTF-8")
```

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Importing the dataset

```{r import, echo=TRUE}
df <- read.csv("carprice.csv")
df
```

Creating the vectors "x" and "y"

```{r Vectors, echo=TRUE}
x <- c(df$Age)
x

y <- c(df$Price)
y
```

Conducting a linear regression

```{r Linear regression, echo=TRUE}
lm1 <- lm(y ~ x)
summary(lm1)
```

Conducting ANOVA test

```{r ANOVA, echo=TRUE}
ANOVA <- aov(y ~ x, df)
summary(ANOVA)
```

Due to the results of the ANOVA test, on the confidence level 95% the P-value is significant. So, there is significant difference betwen the Age and the Price of cars.

Runing the given code (constructing the Sum Sq manually)

```{r Running the code, echo=TRUE}
n <- 11

X <- cbind(1,x)

H <- X%*%solve(t(X)%*%X)%*%t(X)

J <- matrix(1,n,n)

In <- diag(n)

SStotal <- t(y)%*%(In-1/n*J)%*%y

SSreg <-  t(y)%*%(H-1/n*J)%*%y

SSres <- t(y)%*%(In-H)%*%y

SSreg; SSreg
```

Based on the comparing with the results of the ANOVA test, the code that just was run, it calculates the Sum of the Squares of the linear regression model
