---
title: "Lab 5. Networks on Texts. Part 2"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

\begin{center}
National Research University Higher School of Economics,  
Faculty of Social Sciences


{\Large Introduction to Network Analysis, Spring 2019 \par}


\large \textbf{Seminar 5, Part II, 15/02/2019}

Dmitry Zaytsev, PhD and Valentina Kuskova, PhD 

\small{(with deep appreciation to all used sources; references available in text and upon request)}

\end{center}

#2. Parsing and Text Mining for English texts: example of the Protests in Venezuela 2019:
## First, Get links from the GOOGLE search results **protests in venezuela 2019**:
```{r}
library(rvest)
page_use <- read_html("https://www.google.com/search?q=protests+in+venezuela+2019&num=100&newwindow=1&rlz=1C1CHBD_ruRU822RU822&source=lnms&tbm=nws&sa=X&ved=0ahUKEwjy9KXXxbjgAhWp5KYKHWWbDxQQ_AUIDygC&biw=1440&bih=790")
links <- page_use %>% html_nodes(xpath='//h3/a') %>% html_attr('href')
gsub('/url\\?q=','',sapply(strsplit(links[as.vector(grep('url',links))],split='&'),'[',1))

```
## Second, Download in working environment the vector of first 10 links:
```{r}
links2 <- c ("https://www.theguardian.com/world/2019/feb/12/venezuela-guaido-maduro-protest",
"https://ru.euronews.com/2019/02/12/ru-venezuela-protests",
"https://www.cnn.com/americas/live-news/venezuela-protests-2019/index.html",
"https://www.theguardian.com/world/2019/feb/08/venezuela-juan-guaido-central-university-speech-maduro-protests",
"https://www.cnn.com/2019/02/02/americas/venezuela-unrest/index.html",
"https://www.cnn.com/2019/01/29/americas/venezuela-protests-deaths/index.html",
"https://www.theguardian.com/world/video/2019/feb/03/tens-of-thousands-protest-in-venezuela-to-urge-nicolas-maduro-to-resign-video",
"https://www.theguardian.com/world/2019/feb/10/venezuela-maduro-chavez-guaido-protests",
"https://www.cnn.com/2019/01/28/americas/venezuela-unrest-maduro-accusations-guaido/index.html",
"https://montreal.citynews.ca/video/2019/02/12/venezuela-protesters-call-for-emergency-aid/")

```
## Third, Download .html files in the working directory:
```{r}
for(i in 1:length(links2)){
  html_object  <- read_html(links2[i])
  somefilename <- paste0("filenameVE_", i, ".html")
  write_xml(html_object, file = somefilename)
}

```
## Fourth, convert html to text
```{r}
html <- list.files(pattern="\\.(htm|html)$") # get just .htm and .html files
library(tm)
library(RCurl)
library(XML)
htmlToText <- function(input, ...) {
  ###---PACKAGES ---###
  require(RCurl)
  require(XML)
  
  
  ###--- LOCAL FUNCTIONS ---###
  # Determine how to grab html for a single input element
  evaluate_input <- function(input) {    
    # if input is a .html file
    if(file.exists(input)) {
      char.vec <- readLines(input, warn = FALSE)
      return(paste(char.vec, collapse = ""))
    }
    
    # if input is html text
    if(grepl("</html>", input, fixed = TRUE)) return(input)
    
    # if input is a URL, probably should use a regex here instead?
    if(!grepl(" ", input)) {
      # downolad SSL certificate in case of https problem
      if(!file.exists("cacert.perm")) download.file(url="http://curl.haxx.se/ca/cacert.pem", destfile="cacert.perm")
      return(getURL(input, followlocation = TRUE, cainfo = "cacert.perm"))
    }
    
    # return NULL if none of the conditions above apply
    return(NULL)
  }
  
  # convert HTML to plain text
  convert_html_to_text <- function(html) {
    doc <- htmlParse(html, asText = TRUE)
    text <- xpathSApply(doc, "//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)][not(ancestor::form)]", xmlValue)
    return(text)
  }
  
  # format text vector into one character string
  collapse_text <- function(txt) {
    return(paste(txt, collapse = " "))
  }
  
  ###--- MAIN ---###
  # STEP 1: Evaluate input
  html.list <- lapply(input, evaluate_input)
  
  # STEP 2: Extract text from HTML
  text.list <- lapply(html.list, convert_html_to_text)
  
  # STEP 3: Return text
  text.vector <- sapply(text.list, collapse_text)
  return(text.vector)
}
html2txt <- lapply(html, htmlToText)
```
## Fifth, clean out non-ASCII characters
```{r}
html2txtclean <- sapply(html2txt, function(x) iconv(x, "latin1", "ASCII", sub=""))
```
## Sixth, make corpus for text mining
```{r}
corpus <- Corpus(VectorSource(html2txtclean))
```
## Seventh, Let’s check the corpus we recived:
```{r}
tdm_matrix<-TermDocumentMatrix(corpus)
VE_tdm<-as.matrix(tdm_matrix)
dim(VE_tdm)
```

## Eighth, Let's clean put data:
Better to do it in excel:
```{r}
write.csv(VE_tdm, file = "VE.csv")
```
In Excel you can clean the data, and cut not important terms (I chose to cut words with frequencies less than 9, so I leave with 217 most frequent words out of 3677). I cut terms - can not read col.names - I cut them, by multiplication of matrices create TermToTerm matrix. Write it in working directory.

```{r}
library(readxl)
VE_noterms <- read_excel("VE_noterms.xlsx")
VE<-as.matrix(VE_noterms)%*%t(as.matrix(VE_noterms))
dim(VE)
write.csv(VE, file = "VE_matrixwithNOterms.csv")
```
Then, I add terms back, and read it again:
```{r}
library(readr)
VE_matrixwithterms <- read_csv("VE_matrixWITHterms.csv")
dim(VE_matrixwithterms)
```

```{r}
library(network)
net <- as.network(VE_matrixwithterms)
plot(net)
```






